---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

<!-- To add a badge  -->
<!-- [![Travis-CI Build Status](https://travis-ci.org/geanders/countyweather.svg?branch=master)](https://travis-ci.org/geanders/countyweather) -->
<!-- [![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/countyweather)](https://cran.r-project.org/package=countyweather) -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  error = TRUE
)
```

# MclustSepCov

This is a README file of the R package _MclustSepCov_. In our paper available [here](https://www.tandfonline.com/doi/abs/10.1080/02664763.2019.1692795), we analyze the multivariate longitudinal data by applying model-based clustering. We assume the Gaussian mixture model with separable covariance structure where one of covariance factors is assumed to have a temporal structure.

## Installation of the package

To install our package, you may simply execute the following codes:
```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("inmybrain/MclustSepCov", subdir = "MclustSepCov") # don't forget to specify subdir!
```

If you come across a problem like [this](https://github.com/r-lib/remotes/issues/130), please refer to [this answer](https://github.com/r-lib/remotes/issues/130#issuecomment-423830669) in that issue.


Or you can install the source file using the command line after downloading it from [here](https://drive.google.com/uc?export=download&id=1l2q381dgUCr5uBN2Pp6ZjsDOYfF_U3mP);
```{bash, eval = FALSE}
R CMD INSTALL MclustSepCov_1.0.tar.gz
```


## A basic example of using the package
We give a toy example to apply the main function `Mclust_SEP_cpp`. First, generate $40$ samples from the Gaussian mixture model with two components. One of the component has zero mean vector, while the other a vector parallel to $ (1, \cdots, 1)^{\rm T} $ with modulus $5$. We assume the heterogeneous covariance structure between them.

```{r, eval = FALSE}
# install.packages("mvtnorm")
library("MclustSepCov")
K <- 2
p <- 2
q <- 3
U <- lapply(1:K, function(noarg) getCovariance(p, 0.3, "AR"))
V <- lapply(1:K, function(noarg) getCovariance(q, 0.2, "CS"))
Sigma <- Map(kronecker, U, V) # separable covariance matrix
mu <- list(rep(0, p * q), 5 / sqrt(p*q) * rep(1, p * q)) # distinct mean vectors
Y <- vector(mode = "list", length = K)
set.seed(6) # to make results reproducible
for(i in 1:K){
 Y[[i]] <- mvtnorm::rmvnorm(n = 20, mean = mu[[i]], sigma = Sigma[[i]])
}
```

Each list has $20$ samples from each Gaussian component. Candidate models we consider here are the Gaussian mixture distribution with the number of mixture components within $\{1,2,3\}$ and with any of available covariance models.
```{r, eval = FALSE}
fit <- Mclust_SEP_cpp(Y = Reduce(rbind, Y), p = p, q = q, Ks = 1:3, type_cov = "all", save_fit = TRUE)
```

It contains a table showing BIC values for all fitted models.
```{r, eval = FALSE}
fit$bic_table
```

The best model with $2$ components and covariance model 'EEE-ECS' is saved in `best_model`
```{r, eval = FALSE}
fit$best_model
```

If `save_fit=TRUE` (default is `FALSE`), then one can access to all fitted models; for example,
```{r, eval = FALSE}
## VVV-VUN
fit$res_Mclust_SEP$`VVV-VUN`$`1`
fit$res_Mclust_SEP$`VVV-VUN`$`2`
fit$res_Mclust_SEP$`VVV-VUN`$`3`

## EEE-EAR
fit$res_Mclust_SEP$`EEE-EAR`$`1`
fit$res_Mclust_SEP$`EEE-EAR`$`2`
fit$res_Mclust_SEP$`EEE-EAR`$`3`
```

## Notes

- For available covariance structures, see the help page;
```{r, eval = FALSE}
?Mclust_SEP_cpp
```

- As for initial assignment of cluster membership, each sample is assigned randomly to clusters.

## Citation
To cite this package, please use this bibtex format:
```{latex}
@article{Park:2019,
author = {Seongoh Park and Johan Lim and Hyejeong Choi and Minjung Kwak},
title = {Clustering of longitudinal interval-valued data via mixture distribution under covariance separability},
journal = {Journal of Applied Statistics},
volume = {0},
number = {0},
pages = {1-18},
year  = {2019},
publisher = {Taylor & Francis},
doi = {10.1080/02664763.2019.1692795},
URL = { 
        https://doi.org/10.1080/02664763.2019.1692795
},
eprint = { 
        https://doi.org/10.1080/02664763.2019.1692795
}
}
```

## Issues

We are happy to troubleshoot any issue with the package;

- please contact to the maintainer by seongohpark6@gmail.com, or

- please open an issue in the github repository.

<!-- ## Error and warning messages you may get -->
 
<!-- ## References  -->
